%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 8 February 2019
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,]{moderncv}

% moderncv themes
\moderncvstyle{banking}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'

\definecolor{color0}{rgb}{0,0,0}% black
\definecolor{color1}{HTML}{3873B3}% custom
\definecolor{color2}{rgb}{0.45,0.45,0.45}% dark grey

\usepackage[scaled=0.86]{DejaVuSansMono}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\def\donothing#1{#1}
\def\emaillink#1{#1}

%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75,footskip=60pt]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvheadnamewidth}{10cm}            % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...



% personal data
\name{Hao}{Wu}
\title{Data Scientist}
\address{Argus Media}{}{}

 % Phone number
\email{\donothing{\href{mailto:ai910312@gmail.com}{\nolinkurl{ai910312@gmail.com}}}}
 % Personal website


\social[github]{mohowu}




% \extrainfo{additional information}                 % optional, remove / comment the line if not wanted




% Pandoc CSL macros
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}

\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle



\section{Employment}\label{employment}

\nopagebreak
    \cventry{Jan 2022 - Present}{Data Scientist}{}{Argus Media}{}{\begin{itemize}%
\item Successfully delivered a \$250,000  web-based solution for Kuwait Petroleum International (KPI), a major European transport fuel supplier%
\item Building production ready Shiny dashboards for commodity traders using \{golem\} framework%
\item Building custom Shiny inputs using JavaScript to enhance user experience%
\item Manage user permission and data storage with MySQL and AWS S3%
\item Contributing to the data preparation pipeline that feeds into the models forecasting commodity prices and distribution%
\end{itemize}}
    \cventry{Jan 2020 - Jan 2022}{Senior Data Science Specialist}{}{Ricardo Energy \& Environment}{}{\begin{itemize}%
\item Dynamic reporting, data visualisation and building tools for analysing air quality data%
\item Building R Shiny applications integrated with SQL database for data checking and ratification%
\item Building bespoke R packages to simplify the process of data analysis%
\item Using regression and tree based statistical models to predict air quality trends%
\item Building Python CLI tool to scrape and compare data from XML files%
\item Mentoring staff on doing data analysis in R%
\end{itemize}}
    \cventry{Apr 2017 - Jan 2020}{Data Science Specialist}{}{Ricardo Energy \& Environment}{}{\empty}

\section{Education}\label{education}

\nopagebreak
    \cventry{2017}{Ph.D.}{}{University of Edinburgh, UK}{}{\begin{itemize}%
\item Understanding the spatial-temporal variability of urban air pollution%
\item Dispersion and statistical modelling of urban air pollution%
\item Conducting air quality measurements using stationary and portable air quality monitors.%
\end{itemize}}
    \cventry{2013}{BSc (1st Class)}{}{University of Edinburgh, UK}{}{\begin{itemize}%
\item Environmental and Sustainable Chemistry%
\end{itemize}}
    \cventry{2013}{BSc}{}{South China University of Technology, China}{}{\begin{itemize}%
\item Applied Chemistry%
\end{itemize}}

\section{Teaching Experience}\label{teaching-experience}

\nopagebreak
    \cvitem{2019}{Teaching assistant at Ricardo openair and R data analysis training course. London, UK}
    \cvitem{2019}{Teaching assistant at Ricardo openair and R data analysis training course. Huelva, Spain}
    \cvitem{2013 - 2016}{Second Year Physical Chemistry Lab Demonstrator. University of Edinburgh, UK}
    \cvitem{2013 - 2016}{Second Year Environmental Chemistry Lab Demonstrator. University of Edinburgh, UK}

\section{Techinal Skills}\label{techinal-skills}

\subsection{Programming Languages}\label{programming-languages}

\nopagebreak
    \cvitem{Proficient}{R, MySQL, HTML, CSS. }
    \cvitem{Intermediate}{JavaScript, Python. }

\section{Honours and Awards}\label{honours-and-awards}

\nopagebreak
    \cvitem{2016}{Reviewer of Environmental Pollution Journal. }
    \cvitem{2013 - 2016}{Edinburgh Global Research Scholarship. }
    \cvitem{2013}{Undergraduate Research Project Prize. }

\section{Publications}\label{publications}

\phantomsection\label{refs-75d88f064d195362f6ac9937848a54ab}
\begin{CSLReferences}{0}{0}
\bibitem[\citeproctext]{ref-lin_practical_2017}
\CSLLeftMargin{1. }%
\CSLRightInline{Lin, C., Masey, N., Wu, H., Jackson, M., Carruthers, D.
J., Reis, S., Doherty, R. M., Beverland, I., \& Heal, M. R. (2017).
Practical field calibration of portable monitors for mobile measurements
of multiple air pollutants. \emph{Atmosphere}, \emph{8}(12).
\url{https://doi.org/10.3390/atmos8120231}}

\bibitem[\citeproctext]{ref-kenagy_greater_2016}
\CSLLeftMargin{2. }%
\CSLRightInline{Kenagy, H. S., Lin, C., Wu, H., \& Heal, M. R. (2016).
Greater nitrogen dioxide concentrations at child versus adult breathing
heights close to urban main road kerbside. \emph{Air Quality, Atmosphere
\& Health}, \emph{9}(6), 589--595.
\url{https://doi.org/10.1007/s11869-015-0370-3}}

\bibitem[\citeproctext]{ref-wu_effect_2017}
\CSLLeftMargin{3. }%
\CSLRightInline{Wu, H., Reis, S., Lin, C., \& Heal, M. R. (2017). Effect
of monitoring network design on land use regression models for
estimating residential NO2 concentration. \emph{Atmospheric
Environment}, \emph{149}, 24--33.
\url{https://doi.org/10.1016/j.atmosenv.2016.11.014}}

\bibitem[\citeproctext]{ref-wu_identifying_2015}
\CSLLeftMargin{4. }%
\CSLRightInline{Wu, H., Reis, S., Lin, C., Beverland, I. J., \& Heal, M.
R. (2015). Identifying drivers for the intra-urban spatial variability
of airborne particulate matter components and their interrelationships.
\emph{Atmospheric Environment}, \emph{112}, 306--316.
\url{https://doi.org/10.1016/j.atmosenv.2015.04.059}}

\bibitem[\citeproctext]{ref-steinle_personal_2015}
\CSLLeftMargin{5. }%
\CSLRightInline{Steinle, S., Reis, S., Sabel, C. E., Semple, S., Twigg,
M. M., Braban, C. F., Leeson, S. R., Heal, M. R., Harrison, D., Lin, C.,
\& Wu, H. (2015). Personal exposure monitoring of PM2.5 in indoor and
outdoor microenvironments. \emph{Science of The Total Environment},
\emph{508}, 383--394.
\url{https://doi.org/10.1016/j.scitotenv.2014.12.003}}

\end{CSLReferences}


\end{document}

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
