---
author: Hao Wu
title: Data Scientist/Software Engineer
format:
  classic-cv-pdf: default
cvfooter:
  # left: "mr.schochastics.net"
  right: "github.com/mohowu"
cvcolor: 58748F #without `#`
cvfont: raleway #texlive fonts like raleway,fetamont,gillius,comfortaa
cvmeta:
  - title: Status
    left: Data Scientist @ Argus Media
    right: Didcot, UK
  - title: Field
    left: Software Engineering, Data Science
    # right: mr.schochastics.net
  - title: Techs
    left: R, Python, JavaScript, HTML, CSS
    # right: david@schochastics.net
execute:
  echo: false
---

```{r}
#| include: false
library(tibble)
library(dplyr)
library(lubridate)
library(glue)
library(readr)
library(tidyr)
```

```{r}
#| label: cvevents
cvevents <- function(tbl, when, what, where, details) {

    command_start <- "\\cvevent"
    
    # Function to escape LaTeX special characters
    escape_latex <- function(x) {
      x <- gsub("\\{", "\\\\textbraceleft ", x)
      x <- gsub("\\}", "\\\\textbraceright ", x)
      x <- gsub("&", "\\\\&", x)  # Escape ampersand
      x <- gsub("_", "\\\\_", x)  # Escape underscore
      return(x)
    }

    res <- paste0(
        command_start, "{", escape_latex(tbl[[when]]), "}", 
        "{", escape_latex(tbl[[what]]), "}",
        "{", escape_latex(tbl[[where]]), "}")
    
    if (!missing(details)) {
          tbl[[details]] <- sapply(tbl[[details]], function(x) {
            # Escape special characters, then wrap each item in braces
            escaped_items <- sapply(x, escape_latex)
            paste0("{", escaped_items, "}", collapse = ",")
          })
    res <- paste0(res, "{",tbl[[details]],"}")
    } else {
    res <- paste0(res, "{}")
    }
    cat(res, sep = "\n")
}
```

# Summary

**Data Scientist & Software Engineer** with extensive experience in full-stack application development. Expert in operationalising machine learning models and building interactive, data-driven applications using Python and R. Specialized in Generative AI, including the design of RAG pipelines, multimodal embedding strategies, and high-performance vector search optimization. Adept at managing the full lifecycle of data products from research and prototyping to deployment and monitoring.

```{r}
#| include: false
exp <- read_csv("https://docs.google.com/spreadsheets/d/1ETdDJGgHBfp2cYTPwX8GS34xaHrYzo5EIeqNCpmyIw8/export?format=csv") |> 
  fill(start, end, what, where) |>  
  mutate(when = glue("{start} - {end}")) |>
  nest(data = c(why)) |> 
  mutate(tasks = purrr::map(data, ~{unlist(.x) |> as.character()}))

edu <- read_csv("https://docs.google.com/spreadsheets/d/13nOKX19g6xCLdeEzYrrs__gq8XOb4F3HSCzinfEXrQQ/pub?output=csv") |> 
  fill(when, what, where) |>  
  nest(data = c(why)) |> 
  mutate(tasks = purrr::map(data, ~{unlist(.x) |> as.character()}))

te <- read_csv("https://docs.google.com/spreadsheets/d/1qfmOKElJVxr9DtztGl_svM4wBZtoLf8Hfx-aw0Blgfw/pub?output=csv") |> 
  nest(data = c(why)) |> 
  mutate(tasks = purrr::map(data, ~{unlist(.x) |> as.character()}))


pe <- read_csv("https://docs.google.com/spreadsheets/d/1W1OfFuq-46YZGBaZ_euwjv2xPODuW4kJgNGnoG_gKds/export?format=csv") |>
  fill(when, what, where) |>
  nest(data = c(why)) |>
  mutate(tasks = purrr::map(data, ~{unlist(.x) |> as.character()}))

```

# Professional Experience


```{r}
#| label: experience
#| output: asis
#| message: false

exp |> cvevents(when = "when", what = "what", where = "where", details = "tasks")
```

# Education

```{r }
#| label: education
#| output: asis
edu |> cvevents(when = "when", what = "what", where = "where", details = "tasks")
```

# Personal Projects

```{r }
#| label: teaching exp
#| output: asis
pe |> cvevents(when = "when", what = "what", where = "where", details = "tasks")
```

