---
author: Hao Wu
title: Data Scientist/Software Engineer
format:
  classic-cv-pdf: default
cvfooter:
  # left: "mr.schochastics.net"
  right: "github.com/mohowu"
cvcolor: 58748F #without `#`
cvfont: raleway #texlive fonts like raleway,fetamont,gillius,comfortaa
cvmeta:
  - title: Status
    left: Data Scientist @ Argus Media
    right: Didcot, UK
  - title: Field
    left: Software Engineering, Data Science
    # right: mr.schochastics.net
  - title: Techs
    left: R, Python, JavaScript, HTML, CSS
    # right: david@schochastics.net
execute:
  echo: false
---

```{r}
#| include: false
library(tibble)
library(dplyr)
library(lubridate)
library(glue)
library(readr)
library(tidyr)
library(stringr)
```

```{r}
#| label: cvevents
cvevents <- function(tbl, when, what, where, details) {

    command_start <- "\\cvevent"
    
    # Function to escape LaTeX special characters
    escape_latex <- function(x) {
      x <- gsub("\\{", "\\\\textbraceleft ", x)
      x <- gsub("\\}", "\\\\textbraceright ", x)
      x <- gsub("&", "\\\\&", x)  # Escape ampersand
      x <- gsub("_", "\\\\_", x)  # Escape underscore
      return(x)
    }
    
    # Function to escape URLs for LaTeX (minimal escaping - only for special chars in URLs)
    escape_url <- function(x) {
      # URLs in \href should have minimal escaping
      # Only escape characters that break LaTeX syntax
      x <- gsub("\\{", "\\\\{", x)
      x <- gsub("\\}", "\\\\}", x)
      x <- gsub("#", "\\#", x)
      x <- gsub("$", "\\$", x)
      x <- gsub("&", "\\&", x)
      x <- gsub("%", "\\%", x)
      return(x)
    }
    
    # Function to convert markdown links [text](url) to LaTeX \href{url}{text}
    # and escape remaining text that's not part of LaTeX commands
    convert_markdown_links <- function(x) {
      if (is.na(x) || length(x) == 0) {
        return(ifelse(is.na(x), x, ""))
      }
      
      x <- as.character(x)
      if (nchar(x) == 0) {
        return(x)
      }
      
      # Pattern to match [text](url)
      pattern <- "\\[([^\\]]+)\\]\\(([^)]+)\\)"
      
      # Check if there are any matches
      if (!str_detect(x, pattern)) {
        # No links found, just escape the text
        return(escape_latex(x))
      }
      
      # Use stringr's str_replace_all with a function for replacement
      # First, replace links with placeholders
      result <- x
      replacements <- list()
      counter <- 0
      
      # Process all matches
      while (str_detect(result, pattern)) {
        # Extract the first match
        match_text <- str_extract(result, pattern)
        
        # Extract text and URL from the match
        text <- str_match(match_text, pattern)[1, 2]
        url <- str_match(match_text, pattern)[1, 3]
        
        # Escape text and URL
        text_escaped <- escape_latex(text)
        url_escaped <- escape_url(url)
        
        # Create LaTeX command
        latex_cmd <- paste0("\\href{", url_escaped, "}{", text_escaped, "}")
        
****        # Create unique placeholder
        counter <- counter + 1
        placeholder <- paste0("XXXLATEXLINK", counter, "XXX")
        replacements[[placeholder]] <- latex_cmd
        
        # Replace first occurrence
        result <- str_replace(result, pattern, placeholder)
      }
      
      # Escape remaining text
      result <- escape_latex(result)
      
      # Restore LaTeX commands
      for (ph in names(replacements)) {
        result <- str_replace_all(result, fixed(ph), replacements[[ph]])
      }
      
      return(result)
    }
    
    # Process the where column: convert markdown links and escape remaining text
    # Convert each element in the where column
    where_processed <- character(nrow(tbl))
    for (i in seq_along(tbl[[where]])) {
      x <- tbl[[where]][i]
      if (is.null(x) || is.na(x)) {
        where_processed[i] <- ifelse(is.na(x), "", as.character(x))
      } else {
        where_processed[i] <- convert_markdown_links(as.character(x))
      }
    }

    res <- paste0(
        command_start, "{", escape_latex(tbl[[when]]), "}", 
        "{", escape_latex(tbl[[what]]), "}",
        "{", where_processed, "}")
    
    if (!missing(details)) {
          tbl[[details]] <- sapply(tbl[[details]], function(x) {
            # Escape special characters, then wrap each item in braces
            escaped_items <- sapply(x, escape_latex)
            paste0("{", escaped_items, "}", collapse = ",")
          })
    res <- paste0(res, "{",tbl[[details]],"}")
    } else {
    res <- paste0(res, "{}")
    }
    cat(res, sep = "\n")
}
```

# Summary

**Data Scientist & Software Engineer** with extensive experience in full-stack application development. Expert in operationalising machine learning models and building interactive, data-driven applications using Python and R. Specialized in Generative AI, including the design of RAG pipelines, multimodal embedding strategies, and high-performance vector search optimization. Adept at managing the full lifecycle of data products from research and prototyping to deployment and monitoring.

```{r}
#| include: false
exp <- read_csv("https://docs.google.com/spreadsheets/d/1ETdDJGgHBfp2cYTPwX8GS34xaHrYzo5EIeqNCpmyIw8/export?format=csv") |> 
  fill(start, end, what, where) |>  
  mutate(when = glue("{start} - {end}")) |>
  nest(data = c(why)) |> 
  mutate(tasks = purrr::map(data, ~{unlist(.x) |> as.character()}))

edu <- read_csv("https://docs.google.com/spreadsheets/d/13nOKX19g6xCLdeEzYrrs__gq8XOb4F3HSCzinfEXrQQ/pub?output=csv") |> 
  fill(when, what, where) |>  
  nest(data = c(why)) |> 
  mutate(tasks = purrr::map(data, ~{unlist(.x) |> as.character()}))

te <- read_csv("https://docs.google.com/spreadsheets/d/1qfmOKElJVxr9DtztGl_svM4wBZtoLf8Hfx-aw0Blgfw/pub?output=csv") |> 
  nest(data = c(why)) |> 
  mutate(tasks = purrr::map(data, ~{unlist(.x) |> as.character()}))


pe <- read_csv("https://docs.google.com/spreadsheets/d/1W1OfFuq-46YZGBaZ_euwjv2xPODuW4kJgNGnoG_gKds/export?format=csv") |>
  fill(when, what, where) |>
  nest(data = c(why)) |>
  mutate(tasks = purrr::map(data, ~{unlist(.x) |> as.character()}))

```

# Professional Experience


```{r}
#| label: experience
#| output: asis
#| message: false

exp |> cvevents(when = "when", what = "what", where = "where", details = "tasks")
```

# Education

```{r }
#| label: education
#| output: asis
edu |> cvevents(when = "when", what = "what", where = "where", details = "tasks")
```

# Personal Projects

```{r }
#| label: teaching exp
#| output: asis
pe |> cvevents(when = "when", what = "what", where = "where", details = "tasks")
```

****