---
author: Hao Wu
title: Data Scientist/Shiny Developer
format:
  classic-cv-pdf: default
cvfooter:
  # left: "mr.schochastics.net"
  right: "github.com/mohowu"
cvcolor: 58748F #without `#`
cvfont: raleway #texlive fonts like raleway,fetamont,gillius,comfortaa
cvmeta:
  - title: Status
    left: Data Scientist @ Argus Media
    right: Didcot, UK
  - title: Field
    left: Software Engineering, Data Science
    # right: mr.schochastics.net
  - title: Techs
    left: R, JavaScript, HTML, CSS, Python
    # right: david@schochastics.net
execute:
  echo: false
---

```{r}
#| include: false
library(tibble)
library(dplyr)
library(lubridate)
library(glue)
library(readr)
library(tidyr)
```

```{r}
#| label: cvevents
cvevents <- function(tbl, when, what, where, details) {

    command_start <- "\\cvevent"

    res <- paste0(
        command_start, "{", tbl[[when]], "}", 
        "{", tbl[[what]], "}",
        "{", tbl[[where]], "}")
    
    if (!missing(details)) {
          tbl[[details]] <- sapply(tbl[[details]], function(x) paste0("{", x, "}", collapse = ","))
    res <- paste0(res, "{",tbl[[details]],"}")
    }
    cat(res, sep = "\n")
}
```

# Summary

Data Scientist and R Shiny Developer with strong experience in R development. Skilled in creating interactive data visualizations and applications. A quick learner with a good understanding of data analysis, statistical methods, and machine learning. Focused on delivering practical solutions and continuously improving my skills. Enjoy working with data and keeping up with new tools and techniques in the field.

```{r}
#| include: false

exp <- read_csv("https://docs.google.com/spreadsheets/d/1ETdDJGgHBfp2cYTPwX8GS34xaHrYzo5EIeqNCpmyIw8/pub?output=csv") |> 
  fill(start, end, what, where) |>  
  mutate(when = glue("{start} - {end}")) |>
  nest(data = c(why)) |> 
  mutate(tasks = purrr::map(data, ~{unlist(.x) |> as.character()}))

edu <- read_csv("https://docs.google.com/spreadsheets/d/13nOKX19g6xCLdeEzYrrs__gq8XOb4F3HSCzinfEXrQQ/pub?output=csv") |> 
  fill(when, what, where) |>  
  nest(data = c(why)) |> 
  mutate(tasks = purrr::map(data, ~{unlist(.x) |> as.character()}))

te <- read_csv("https://docs.google.com/spreadsheets/d/1qfmOKElJVxr9DtztGl_svM4wBZtoLf8Hfx-aw0Blgfw/pub?output=csv") |> 
  nest(data = c(why)) |> 
  mutate(tasks = purrr::map(data, ~{unlist(.x) |> as.character()}))

```

# Experience


```{r}
#| label: experience
#| output: asis
#| message: false

exp |> cvevents(when = "when", what = "what", where = "where", details = "tasks")
```

# Education

```{r }
#| label: education
#| output: asis
edu |> cvevents(when = "when", what = "what", where = "where", details = "tasks")
```

# Teaching Experience

```{r }
#| label: teaching exp
#| output: asis
te |> cvevents(when = "when", what = "what", where = "where", details = "tasks")
```

